# __CS 329E: Project 1__

Due: February 4, 2015

Students: Jiannan Zhang & Jaclyn Nguyen

========================================================

This project required us to pull data from a RestfulReL server and explore the data.Below shows the step by step process of exploring and reproducing the required visualization for Project1 Requirements.


__1. Loading of necessary R packages: RCurl, ggplot2 (R code not shown)__

```{r, include=FALSE}
library(RCurl)
library (ggplot2)
```

__2. Creation of data frames for each data set: "df_cust","df_orders", "df_ord_details", "df_items"__

```{r}
# data frame #1 (df1)
source("../Data/df_cust.R", echo = TRUE)
```
Below shows a sample of the data set "df_cust" and a ggplot representing
the customers and the state in which they reside in.

```{r}
head(df_cust)

# plot1 part A for df_cust
source("../Visualizations/plot1pta.R", echo = TRUE)

#plot1 part B recreates visual above, but using a histogram instead to repsent the data
source("../Visualizations/plot1ptb.R", echo = TRUE)
```

Below shows a sample of the data set "df_orders" and a ggplot representing
the customers and their associated order id number.
```{r}
# data frame #2 (df2)
source("../Data/df_orders.R", echo = TRUE)
head(df_orders)
# plot2 for df_orders
source("../Visualizations/plot2.R", echo = TRUE)
```

Below shows a sample of the data set "df_ord_detail" and a ggplot representing the item number and the order quantity. Each point represents one order, where the y-axis showcases the quatitiy per order.
```{r}
# data frame #3 (df3)
source("../Data/df_ord_details.R", echo = TRUE)

#plot3
source("../Visualizations/plot3.R", echo = TRUE)

```

Below shows a sample of the data set "df_items" and a ggplot representing
the item number, pricing, and artist association.
```{r}
# Data Frame #4 (df4)
source("../Data/df_items.R", echo = TRUE)

#plot4
source("../Visualizations/plot4.R", echo = TRUE)
```

__3. The next R code merges the four data frames into one data frame that allows us to reproduce the visuals from Project 1 Requirements__
```{r, warning=FALSE}
source("../Data/df_main.R", echo = TRUE)

# plot1 based on Unit Price
source("../Visualizations/plot1up.R", echo = TRUE)

# plot2 based on TITLE
source("../Visualizations/plot1title.R", echo = TRUE)

# plot3 based on ARTIST
source("../Visualizations/plot1artist.R", echo = TRUE)

```{r fig.width=7, fig.height=6}
```

