# __CS 329E: Project 1__

Due: February 4, 2015

Students: Jiannan Zhang & Jaclyn Nguyen

========================================================

This project required us to pull data from a RestfulReL server and explore the data.Below shows the step by step process of exploring and reproducing the required visualization for Project1 Requirements.


__1. Loading of necessary R packages: RCurl, ggplot2 (R code not shown)__

```{r, include=FALSE}
library(RCurl)
library (ggplot2)
```

__2. Creation of data frames for each data set: "df_cust","df_orders", "df_ord_details", "df_items"__

```{r}
# data frame #1 (df1)
source("../Data/df_cust.R", echo = TRUE)
```
Below shows a sample of the data set "df_cust" and a ggplot representing
the customers and the state in which they reside in.

```{r}
head(df_cust)

# plot1 part A for df_cust
ggplot (df_cust, aes(x = CUSTOMER_STATE, y = CUSTOMER_LAST_NAME)) + geom_point()

#plot1 part B recreates visual above, but using a histogram instead to repsent the data
ggplot (data = df_cust) + geom_histogram(aes(x = CUSTOMER_STATE))
```

Below shows a sample of the data set "df_orders" and a ggplot representing
the customers and their associated order id number.
```{r}
# data frame #2 (df2)
source("../Data/df_orders.R", echo = TRUE)
head(df_orders)
# plot2 for df_orders
ggplot(df_orders, aes(x = CUSTOMER_ID, y = ORDER_ID, color = CUSTOMER_ID)) + geom_point()
```

Below shows a sample of the data set "df_ord_detail" and a ggplot representing the item number and the order quantity. Each point represents one order, where the y-axis showcases the quatitiy per order.
```{r}
# data frame #3 (df3)
source("../Data/df_ord_details.R", echo = TRUE)

#plot3
ggplot(df_ord_details, aes(x = ITEM_ID, y = ORDER_QTY)) + geom_point() + scale_x_discrete(breaks=df_ord_details$ITEM_ID)
#hist(df_ord_details$ITEM_ID)
```

Below shows a sample of the data set "df_items" and a ggplot representing
the item number, pricing, and artist association.
```{r}
# Data Frame #4 (df4)
source("../Data/df_main.R", echo = TRUE)

#plot4
ggplot(df_items, aes(x = ITEM_ID, y = UNIT_PRICE, color = ARTIST)) + geom_point() + scale_x_discrete(breaks = df_items$ITEM_ID)
```

__3. The next R code merges the four data frames into one data frame that allows us to reproduce the visuals from Project 1 Requirements__
```{r, warning=FALSE}
df_main <- df <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from orders o join customers c on o.customer_id = c.customer_id join order_details d on o.order_id = d.order_id join items i on d.item_id = i.item_id"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))

# plot1 based on Unit Price
ggplot(df_main, aes(x = as.Date(ORDER_DATE,"%Y-%m-%d"), y = as.Date(SHIPPED_DATE,"%Y-%m-%d"), color = as.factor(UNIT_PRICE)) ) + geom_point() + facet_wrap(~CUSTOMER_STATE)

# plot2 based on TITLE
ggplot(df_main, aes(x = as.Date(ORDER_DATE,"%Y-%m-%d"), y = as.Date(SHIPPED_DATE,"%Y-%m-%d"), color = as.factor(TITLE)) ) + geom_point() + facet_wrap(~CUSTOMER_STATE)

# plot3 based on ARTIST
ggplot(df_main, aes(x = as.Date(ORDER_DATE,"%Y-%m-%d"), y = as.Date(SHIPPED_DATE,"%Y-%m-%d"), color = as.factor(ARTIST)) ) + geom_point() + facet_wrap(~CUSTOMER_STATE)

```{r fig.width=7, fig.height=6}
```

